---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

First we are going to load some data. It represents two months of data from an anonymous individual collected during the months of October and November, 2012 and include the number of steps taken in 5 minute intervals each day.  The dataset was downloaded from https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip and extracted to the working directory to start the project.

Activity monitoring data [52K]
 * steps: Number of steps taking in a 5-minute interval (missing values are coded as NA)
 * date: The date on which the measurement was taken in YYYY-MM-DD format
 * interval: Identifier for the 5-minute interval in which measurement was taken

The dataset is stored in a comma-separated-value (CSV) file and there are a total of 17,568 observations in this dataset.

```{r}
steps <- read.csv("activity.csv")
```

Let's summarize the activity data and take a look at its limits.

```{r}
summary(steps)
```


## What is mean total number of steps taken per day?



## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
